\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-06 paper.tex
Improve discussion introduction, reshuffle its organisation

\section{Discussion: when Artificial Intelligence enables Human-Robot
Interaction}
\label{sect|conclusion}

This last section summarises our main contributions and tries to clarify the ``take home'' message: what are the challenges
that human-robot interaction brings to artificial intelligence, and what is the
current state-of-the-art in this field?

\subsection{The Key Issues}

We would like first to restate the main challenges to artificial intelligence
raised by human-robot interaction.

\subsubsection{Embodied Cognition}

@@

>>>>

\section{Discussion: When Artificial Intelligence Enables Human-Robot
Interaction}
\label{sect|conclusion}

This last section tries to clarify the ``take home'' message: what are the challenges
that human-robot interaction brings to artificial intelligence, and what is the
current state-of-the-art in this field?

We first restate the challenge of \emph{embodied cognition} and list what we
seen as the main decisional issues that need to be tackled to push forward
human-robot interaction. We then reflect on the importance of knowledge handling
in modern robotics and put our choice of the RDF formalism into perspective.
Finally, we briefly re-discuss two facets of HRI: the importance of
\emph{modelling the humans}, and the difficulty of \emph{acting in presence of
humans}.

\subsection{Embodied Cognition}

@@

\subsection{The Key Decisional Issues}

How can we restate the main challenges, in particular in term of decision
making, that human-robot interaction brings to artificial intelligence?
